Revision of MS #2018:11:32569:0:0:REVIEW

### 2019-02-10 docs/reviews.Rmd
Updated line numbers and added all of Seans comments in responses to reviewers

*The text now correctly states the research was performed in the Bahamas (L37).*

@@

*"impacts" has been replaced with "negative effects" in L47, now L48*

@@

*We have improved the wording in the original sentence and no longer use the word "know"/"known" (L59).*

@@

*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L80-81) and Table 2 (now Table 1) reflect these changes.*

@@

*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L119.*

@@

*We have included the URL in the main text (L128), but the decision to leave it there depends on the editorial formatting. However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*

@@

*That is correct. We have modified the text to that it reads "each of the different pairs of parameters".*

@@

*Here we report the mean $\pm$ standard deviation of the estimated weights for the 109 organisms from the central Mexican Caribbean. We have modified the text to clarify our point.*

<!-- OK I actually think this is still a very confusing paragraph. It still feels unclear what means +/- SDs we're reporting. Perhaps something like this will clarify: "There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters (F17;1943 = 24:96; p < 0:001). For example, the actual observed weights of the 109 lionfish from the Central Mexican Caribbean had a mean +/- SD of 52.56 +/- 76.58 g. However, if we used allometric parameter values from Banco Chinchorro in the Caribbean to predict weights from our observed length observations, we estimated a mean +/ SD of 40.37  58.74 g (Sabido-Itza´ et al., 2016). If we similarly used parameter values from NORTH CAROLINA (?) to estimate lionfish weights in the Central Mexican Caribbean, we found a mean +/- SD of 73.76  96.11 g (Barbour et al., 2011). These were the two most extreme sets of parameters, but results consistently varied across sites. Weights predicted from these extreme parameters corresponded to predicted-to-observed weight ratios of 0.80  0.19 and 1.76  0.50 (mean  SD), respectively, and the under- and overestimations FOR LIONFISH THAT WERE 310 MM IN TL (the maximum TL in this study) (??) resulted in ratios of 0.36 and 3.51 of the actual observed weight. Ex situ parameter use can therefore result in highly erroneous weight estimates for lionfish. -->

@@

*The figure caption now includes the following sentence: For Sabido-Itza et al, 2016b, BC and PNAX make reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak, two sites for which they report parameters.*

<!-- You gotta tell me how to pronouce Xcalak -->
### Discussion:

@@

*Yes, we refer to the spatial heterogeneity. We have modified the text so it reads "...lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and..."*

@@

*This was meant to say "We show that", and has now been corrected.*

@@

*Other studies do not report the time of the year when these were collected. However, we recognize this may be a factor that influences weight or growth and therefore the length-weight relationship. We have mentioned that our parameters for the Central Mexican Caribbean are from organisms collected during the Summer (L94), and have devoted a paragraph in the discussion (L175) to highlight the importance of collection methods and timing when estimating length-weight relationships.*

@@

*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and as you noted data from Fogg et al. (2013) produced some of the largest estimates. After a careful evaluation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders. The corresponding modifications have been made in the text. Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*

<!-- I don't think you satisfactorily answered this one - you kind of skirted the reviewer's question of how you adjusted for spineless weight (the answer is we didn't, right?).  Don't think you can get away with just saying "The corresponding modifications have been made in the text." -->

@@

*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L175).*

*In terms of the OLS regression versus a mixed modeling approach: in our original manuscript we failed to clearly articulate that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2). We agree that a GLMM with location modeled as a random effect would properly estimate the "location effect" of the length-weight relationship across the different study sites, both by identifying whether differences exist and by describing the magnitude of these differences. Unfortunately, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data - both of which were outside the scope of this study. The fact that similar comments were raised by Rev2 suggests that we did not adequately describe this limitation in our original manuscript. We now explicitly state that we did not have access to the raw data from the published studies (LINES). However, it is important to note that the objective of our study was not to describe the biological differences in length-weight relationships between site locations, rather to assess the effect of using ex situ vs. in situ parameter values to estimate lionfish weights from direct length observations (i.e., to assess whether ex situ parameter values result in large errors in weight estimates). We believe that after modifying the text to clearly state our objectives (LINES - WE MENTION RAW DATA A FEW TIMES NOW, SO INCLUDE EVERY INSTANCE SO IT LOOKS LIKE WE WERE REALLY THOROUGH) and including a discussion paragraph about the limitations of our study (LINES), we have satisfactorily addressed these concerns.*

@@

*We now use the word "key".*

@@

*The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters. We have included a paragraph in the discussion that touches on this (L 185).*
<!-- Be more specific than "touches on this" - quote exactly what you wrote to alleviate the reviewer's concerns -->

<!-- Also I think I said "you" a lot instead of "the reviewer" - my bad.  Change it to whatever you want, but make it consistent -->

@@

*In terms of ANCOVA use: this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates. As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations. However, we do not have the raw data from other studies and applying this to the predicted estimates would not help us answer this question. In a sense, we would be asking if the lines in Fig 3 (with no variation around them) have significantly different slopes and intercepts. As mentioned in the response to R1, we originally failed to clearly state that we do not have the raw data required to perform such an analysis. We have included statements in the methods (LINES) and a discussion paragraph (L175) that highlight these limitations and clarify our objectives/analyses.*
<!-- General point - never use the word "this" to end a sentence - you always want to follow "this" with another word (e.g., "highlighting this topic" instead of "highlighting this") -->

@@

*We have included the log-log version of Figure 3 in the appendices as Supplementary Figure 1. We reference such figure in the caption to Figure 3.*
<!-- Don't you think we should include the Central Mexican Caribbean in Fig 3 and Fig S1? -->
Figure 3, showing the untransformed data, should be amended so that each fitted curve extends across the range of total lengths specific to that study.

@@

*As stated above, these were also raised by Rev1. We believe that our modifications to the discussion in lines... now explicitly mention these issues. And while we cannot test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*
<!-- modification in which lines? -->
<!-- Alright we gotta do a better job on this one - s/he says this is THE area for major improvement. I think the text is mostly there in the manuscript now, but we need to specifically answer each of the questions the reviewer asks, preferably while quoting the text as well -->

@@

*We have corrected this and now refer to four and six studies. These are now in L83 and L85.*

@@

*We believe that gear selectivity is effectively eliminated because all observed organisms were collected. When pole spears are used, it is difficult to sample organisms that are smaller than 50 mm. This might explain why most of the studies show higher minimum lengths. We believe that the Supplementary Table 2 now addresses this and makes all the reviewed information available to future readers.*
<!-- I don't understand the logic in the first sentence - why does collecting them elimiate gear selectivity concerns? -->
5. Methods: There is no need to include equation (3). The weight-length relationship in fishes is simply modeled as a power function, which can be log-transformed to generate a linear relationship. This is clear from equations (1) and (2), in fact, the log-transformation of this power function is standard enough that equation (2) does not likely need to appear in the manuscript, instead simply state the function was linearized using log-transformation.
<!-- Maybe this reviewer would disagree with my idea to add the ANCOVA equation... What do you think? -->
*We have modified the text and now only include Eq 1.*

6. Table 1 is not necessary as all of the included information is presented in Figure 2 or in the body of the text. Related to this, only include information on the weight-length relationship from the central Mexican coast in the text that is not already presented in Figure 2; there is no need to include it in two places.
<!-- Ok well given this, I guess also ignore my comment that I thought we should include this study in Fig 3 and S1 -->
*We agree, and have now removed Table 1.*

7. Results line 140: stated predicted/observed ratios were 0.36 – 3.51, but in the sentences above the authors state the lowest was 0.80 and the highest was 1.76; if the above are means and the 0.36 – 3.51 refers to individual fish, this needs to be made clear, but I think reporting the means is sufficient, and most appropriate; particularly if the ANCOVA applied to the full relationships makes the analysis of the predicted/observed ratios redundant, and it is removed. Reporting the range in mean ratios would be sufficient along with an illustrative figure.
<!-- Already commented on this in the manuscript - but are those extremes (.36 and 3.51) for lionfish that are length 310 mm? Need to be clear about that -->
*That is correct, the 0.80 and 1.76 values make reference to the mean ratios. We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51 - especially because we are unable to assess the full length-weight relationships from all studies given our lack of raw data. We believe the new text justifies including these extremes.*

8. Remove the column for parameter c from Table 2. a = 10c, so there is no need to show both a and c in the Table. Change Fit to R2 in the Table heading, so it doesn’t need to be defined in the caption.
<!-- I can't knit for some reason, so I can't tell if this was done but I assume you took care of it.  Also isn't it b, not c? -->
*We have removed parameter c from Table 2 (Now Table 1) and modified the header so it has $R^2$.*

@@

*Figure 3 shows a total of 18 lines. This is because from the 12 reviewed papers, a total of 17 relationships were identified BECAUSE OF SEX-SPECIFIC REPORTING AND SOME STUDIES REPORTING MULTIPLE LOCATIONS?? (if so, say that). The additional relationship is the one estimated in this study.*

<!-- Oh wait - you do include this study in Fig 3 - so ignore BOTH of my previous comments haha- but the line for this study needs to be in the figure legend! -->

>>>>

*The text now correctly states the research was performed in the Bahamas.*

@@

*"impacts" has been replaced with "negative effects" in L47, now L49*

@@

*We have improved the wording in the original sentence and no longer use the word "know"/"known". The paragraph now starts in L59.*

@@

*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L81-82) and Table 2 (now Table 1) reflect these changes.*

@@

*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120.*

@@

*We have included the URL in the main text (L129), but the decision to leave it there depends on the editorial formatting. However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*

@@

*That is correct. We have modified the text to that it reads "each of the different pairs of parameters" (L137)*

@@

*We have reworded the paragraph to make it more clear. Specifically, we report the smallest and largest mean estimated weights for the 109 organisms from the central Mexican Caribbean. We then report their corresponding mean predicted-to-observed ratios, which are still averaged for each pair of parameters across all organisms. These correspond to the first and last "violins" in Fig 4. We then provide the extreme values of predicted-to-observed ratios for all organisms and all studies; In a sense, the worst relative over- and underestimations (the smallest and largest values shown in Fig.4 overall). Finally, we provide similar measures for estimated total biomass (that is, the summ of the 109 predicted weights) by study, relative to the actual true observed total biomas. This last measure is now presented in Fig 5.*

@@

*The figure caption now includes the following sentence: For Sabido-Itza et al, 2016b, BC and PNAX make reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak, two sites for which they report parameters. We have also modified the graph so that colors represent regions.*

### Discussion:

@@

*Yes, we refer to the spatial heterogeneity. We have modified the text so it reads "...lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and...". This is now L161.*

@@

*This was meant to say "We show that", and has now been corrected in what is now L162.*

@@

*Other studies do not report the time of the year when these were collected. However, we recognize this may be a factor that influences weight or growth and therefore the length-weight relationship. We have mentioned that our parameters for the central Mexican Caribbean are from organisms collected during the Summer (L101), and have devoted a paragraph in the discussion (L185) to highlight the importance of collection methods and timing when estimating length-weight relationships.*

@@

*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and as Reviewer 2 noted, data from Fogg et al. (2013) produced some of the largest estimates. After a careful evaluation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders. That is, the wording in their paper confused us and made us think they reported spineless weight, but they report total weight. The corresponding modifications have been made in the text. Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*

@@

*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L185).*

*In terms of the OLS regression versus a mixed modeling approach: in our original manuscript we failed to clearly articulate that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2). We agree that a GLMM with location modeled as a random effect would properly estimate the "location effect" of the length-weight relationship across the different study sites, both by identifying whether differences exist and by describing the magnitude of these differences. Unfortunately, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data - both of which were outside the scope of this study. The fact that similar comments were raised by Rev2 suggests that we did not adequately describe this limitation in our original manuscript. We now explicitly state that we did not have access to the raw data from the published studies (L87, L117 and L189). However, it is important to note that the objective of our study was not to describe the biological differences in length-weight relationships between site locations, rather to assess the effect of using ex situ vs. in situ parameter values to estimate lionfish weights from direct length observations (i.e., to assess whether ex situ parameter values result in large errors in weight estimates). We believe that after modifying the text to clearly state our objectives (L87, L117 and L189) and including discussion paragraphs about the limitations of our study (L185 and 196), we have satisfactorily addressed these concerns.*

@@

*We now use the word "key" (L208).*

@@

*The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters. We have included a paragraph in the discussion where we compare our range of TLs (34 - 310 mm) to the ranges used by different studies to estimate their parameters (Paragraph starts in L 196). We also make reference to a new supplementary table where we report all information recorded in other studies.*

@@

*In terms of ANCOVA use: this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates. As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations. However, we do not have the raw data from other studies and applying this to the predicted estimates would not help us answer this question. In a sense, we would be asking if the lines in Fig 3 (with no variance / process error around them) have significantly different slopes and intercepts. As mentioned in the response to R1, we originally failed to clearly state that we do not have the raw data required to perform such an analysis. We have included statements in the methods (L87, L117 and L189) and a discussion paragraph (L185) that highlight these limitations and clarify our objectives/analyses.*

@@

*We have included the log-log version of Figure 3 in the appendices as Supplementary Figure 1. We reference such figure in the caption to Figure 3.*

Figure 3, showing the untransformed data, should be amended so that each fitted curve extends across the range of total lengths specific to that study.

@@

*As stated above, these were also raised by Rev1. We believe that our modifications to the discussion in L185 and L196 now explicitly mention these issues. And while we cannot test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*

*More specifically, paragraph starting in L176 mentions that the spatial patterns in length-weight relationships i) ressemble those observed for length-at-age (Pusack et al 2016), ii) Groups identified by post hoc tests aligned with the spatial distribution of examined studyes and ii) These groups also correspond to genetic analyses (Betancur-R et al 2011).*

*In the new paragraph starting in L185 we now mention that variation can also be caused by other factors that are not related to space. These include different sampling methods, seasonality, and depth ranges.*

@@

*We have corrected this and now refer to four and six studies. The sentence now starts in L94.*

@@

*Hand nets allow us to sample all organisms, independent of their sizes. We believe that gear selectivity is effectively eliminated because all observed organisms were collected. When pole spears are used, it is difficult to sample organisms that are smaller than ~50 mm. This might explain why most of the studies show higher minimum lengths. We believe that the Supplementary Table 2 now addresses this and makes all the reviewed information available to future readers.*

5. Methods: There is no need to include equation (3). The weight-length relationship in fishes is simply modeled as a power function, which can be log-transformed to generate a linear relationship. This is clear from equations (1) and (2), in fact, the log-transformation of this power function is standard enough that equation (2) does not likely need to appear in the manuscript, instead simply state the function was linearized using log-transformation.

*We have modified the text and now only include Eq 1. when talking about allometric growth.*

6. Table 1 is not necessary as all of the included information is presented in Figure 2 or in the body of the text. Related to this, only include information on the weight-length relationship from the central Mexican coast in the text that is not already presented in Figure 2; there is no need to include it in two places.

*We agree, and have now removed Table 1.*

7. Results line 140: stated predicted/observed ratios were 0.36 – 3.51, but in the sentences above the authors state the lowest was 0.80 and the highest was 1.76; if the above are means and the 0.36 – 3.51 refers to individual fish, this needs to be made clear, but I think reporting the means is sufficient, and most appropriate; particularly if the ANCOVA applied to the full relationships makes the analysis of the predicted/observed ratios redundant, and it is removed. Reporting the range in mean ratios would be sufficient along with an illustrative figure.

*That is correct, the 0.80 and 1.76 values make reference to the mean ratios. We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51 - especially because we are unable to assess the full length-weight relationships from all studies given our lack of raw data. We believe the new text justifies including these extremes. The paragraph now starts in L136.*

8. Remove the column for parameter c from Table 2. a = 10c, so there is no need to show both a and c in the Table. Change Fit to R2 in the Table heading, so it doesn’t need to be defined in the caption.

*We have removed parameter c from Table 2 (Now Table 1) and modified the header so it has $R^2$.*

@@

*Figure 3 shows a total of 18 lines. This is because from the 12 reviewed papers, a total of 17 relationships were identified because of sex-specific reporting and some studies reporting multiple locations. The additional relationship is the one estimated in this study.*
